---
name: Dr. med. Wojciech
surname: Francuzik
position: "Digital Clinician Scientist"
address: "Dept. of Dermatology, Charité – Universitätsmedizin Berlin"
phone: "+49 30 450 618 344"
www: "fracoscientific.com"
email: "wojciech.francuzik@charite.de"
twitter: wolass
github: wolass
orcid: 0000-0001-5361-9876
profilepic: face2.jpg
linkedin: "wojciech-francuzik"
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::moderncv:
    includes:
      in_header: header.txt

---

\small

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)

```



# Personal data

```{r}
library(tibble)
tribble(
  ~ What, ~ Value, ~ Where,
  "Date of birth", "12. March 1988", "Poznań, Poland",
  "Current position", "Postdoctoral Digital Clinician Scientist and Dermatologist in training", "Charité – Universitätsmedizin Berlin, corporate member of Freie Universität Berlin and Humboldt-Universität zu Berlin, Department of Dermatology, Venereology and Allergology, Div. Allergy and Immunology, Charitéplatz 1, 10117 Berlin, Germany",
  "Nationality", "Polish", ""
) %>%
  detailed_entries(Value, What, Where)
```

\section{Education and Experience}
\cventry{since 01.2023}{Digital Clinician Scientist}{Berlin Institute of Health (BIH) Program}{bihealth.org}{}{}
\cventry{06.2022}{Doctor of Medical Sciences (dr n. med.) degree (with distinction)}{\href{http://kolegianauk.ump.edu.pl/Nadane-stopnie-naukowe-doktora}{Risk factors for postoperative complications in gastrointestinal surgery and the effectiveness of mobile technology in their monitoring}}{Karol Marcinkowski Medical University in Poznań}{}{}
\cventry{01.03.2019}{Doctor of Medicine degree (Dr. med.)}{\href{https://refubium.fu-berlin.de/bitstream/handle/fub188/23991/Diss_Francuzik_.pdf}{Risk factors for a severe reaction in anaphylaxis}}{Magna cum laude}{Clinic for Dermatology, Venereology and Allergology, Charité Universitätsmedizin Berlin}{}
\cventry{01.2019}{Co-founder of the Company}{Warmie Sp. z o.o.}{}{}{}
\cventry{since 01.2018}{Resident Doctor (Assistenzarzt)}{Clinic for Dermatology, Venereology and Allergology, Charité Universitätsmedizin Berlin}{}{}{}
\cventry{since 01.2017}{Chief Scientific Officer}{Medigent Foundation}{Poznań}{}{}
\cventry{01.2017 -- 12.2017}{Research Associate}{Clinic for Dermatology, Venereology and Allergology, Charité Universitätsmedizin Berlin}{}{}{}
\cventry{01.2015 -- 03.2019}{PhD Candidate}{Research Group of Prof. Margitta Worm, Clinic for Dermatology, Venereology and Allergology, Charité Universitätsmedizin Berlin}{}{}{}
\cventry{10.2013 -- 11.2014}{Medical Internship}{2nd Clinical Hospital in Poznań}{Poznań}{}{}
\cventry{2007--2013}{Studies at the Faculty of Medicine I}{Medical University of Poznań}{Poznań}{}{}
\newpage{}
\section{Awards}
\cvitem{02.2022}{\textbf{DGAKI | 1. Mainzer Abstract-Preis 2022} Serological biomarkers of anaphylaxis}{}
\cvitem{04.2019}{\textbf{Poster Prize - EAACI Allergy School} \textit{Insect venom elicited anaphylaxis, a prospective cohort study from the European Anaphylaxis Registry}}{}
\cvitem{2010}{ \emph{PUMS Research Grant of the Student Scientific Society} }
\cvitem{2011 -- 2013}{ \emph{Three awards for the best presentation in the session during the "International Congress of Young Medical Scientists'' in the dermatology session} }

\section{Additional Courses}
\cventry{2019 -- 2021}{Data Scientist}{\href{https://www.datacamp.com/portfolio/wolass}{Datacamp.com}}{}{}{}
\cventry{08.2018}{Good Clinical Practice (GCP-ICH)}{Charité Universitätsmedizin Berlin}{}{}{}
\cventry{04.2016}{Good Scientific Practice (GSP)}{Charité Universitätsmedizin Berlin}{}{}{}
\cventry{2013}{Data analysis}{Johns Hopkins Bloomberg School of Public Health}{Coursera}{}{8 weeks}
\cventry{2013}{Computing for Data Analysis}{Johns Hopkins Bloomberg School of Public Health}{Coursera}{ \textit{with distinction}}{4 weeks}
\cventry{12.2012}{Writing Great Papers in International Journals}{Wiley Science}{University of Warsaw}{}{}
\cventry{2012}{Vaccine Trials: Methods and Best Practices}{Johns Hopkins School of Public Health}{Coursera}{}{7 weeks}


\section{Extra-Curricular Activities}
\cvitem{since 2022}{\textit{Vice Chairman} \textbf{Anaphylaxie Arbeitsgruppe | DGAKI}}
\cvitem{since 2019}{\textit{Member} \textbf{German Society for Allergy and Clinical Immunology}}
\cvitem{since 2018}{\textit{Member} \textbf{European Academy of Allergy and Clinical Immunology}}
\cvitem{since 2016}{\textit{Ambassador} \textbf{Center for Open Science}, COS.io}
\cvitem{since 2015}{\textit{Member} \textbf{Foundation for Open Access Statistics (FOAS)}}
\cvitem{2012--2013}{\textit{Member} \textbf{European Society for Laser Dermatology}}}
\cvitem{2009--2013}{\textit{Member} \textbf{Organizing Committee of the "International Congress of Young Medical Scientists'' organized by the Student Scientific Society}}
\cvitem{2009--2013}{\textit{Member} \textbf{Student Scientific Society of the Medical University of Poznań}}

\section{Language Proficiency}
\cvitemwithcomment{Polish}{native language}{}
\cvitemwithcomment{English}{fluent}{}
\cvitemwithcomment{German}{B2 Certificate, Goethe-Institut}{05.2014}

\section{Bibliometrics}

\cvitemwithcomment{citations}{981}{\href{https://scholar.google.pl/citations?user=-g2ypzoAAAAJ&hl=en}{Google Scholar}}
\cvitemwithcomment{h-index}{16}{\href{https://scholar.google.pl/citations?user=-g2ypzoAAAAJ&hl=en}{Google Scholar}}
\cvitemwithcomment{i10-index}{22}{\href{https://scholar.google.pl/citations?user=-g2ypzoAAAAJ&hl=en}{Google Scholar}}
\cvitemwithcomment{RG-score}{430}{\href{https://www.researchgate.net/profile/Wojciech-Francuzik/stats}{ResearchGate.net}}


```{r fig.width=6, fig.height=3, echo=FALSE}
data <- data.frame(
  year = c(2017:2024),
  citations = c(25, 54, 84, 93, 189, 206, 242, 63),
  publications =  c(5,5,6,9,11,6,8,2)
)

ggpubr::ggarrange(
  data %>% 
  ggpubr::ggbarplot(
    x = "year",
    y = "citations",
    fill = "navy"
    ),
  data %>% 
  ggpubr::ggbarplot(
    x = "year",
    y = "publications",
    fill = "navy"
    )
)

```

**Figure 1.** Citations per year according to Google Scholar.
